# Reproducible Research: Peer Assessment 1
========================================================


```{r setoptions, echo=FALSE}
opts_chunk$set(echo=TRUE)
```

## Loading and preprocessing the data

_**1 - Load the data**_
* Setup the working directory.
* File activity.zip contains data, Unzip the file to the same directory.
* Read the data from activity.csv file by using the read.csv command.
* Missing readings are denoted by NA.


```{r dataloading}
setwd("D:\\T400\\Documents and Settings\\user\\Dropbox\\Coursera\\5 Reproducible Research\\Project1")
unzip( "repdata_data_activity.zip")
data <- read.csv("activity.csv", header=TRUE, na.strings="NA")
``` 

_**2 - Transform the data to a suitable analysis data type / format**_

```{r datatransform}
 data <- transform(data, date = as.Date( date, "%Y-%m-%d"))
 str(data)
```

## What is mean total number of steps taken per day?

_**1 - Explore the data set**_
* Remove NA values

```{r removeNA}
data <- na.omit(data)
```

* Aggregate and explore the new shape of the data.

```{r aggregation}
agg <- with(data, aggregate( steps ~ date, FUN=sum))
with(agg, hist(steps, breaks=55) )
```

_**2 - Calculating the mean and median for the daily steps**_
* Using mean and median of the data set we get these values.

```{r gettingmean, results="asis"}
meantot <- mean(agg$steps)
mediantot <- median(agg$steps)
```
* Mean   : **`r meantot`**
* Median : **`r mediantot`**


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?





